Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-04-01 article-models-main.tex
reorganizing the notes
placed the section on the model type theory in a separate file
separating the constructors section into a separate file
added intro to part II

\vspace{2\baselineskip}
The project proposal is described in \autoref{stage1} and \autoref{stage2}. In
the appendices we give elaborations on the topics discussed in the proposal itself.
By including these we intend to clarify the proposal and present some of the 
(unfinished) work that is already done.

@@

\newpage
\appendix
\input{article-models-tt}

>>>>

\part{Introduction}
The project proposal is described in \autoref{stage1} and \autoref{stage2}. In
the appendices we give elaborations on the topics discussed in the proposal itself.
By including these we intend to clarify the proposal and present some of the 
(unfinished) work that is already done.

@@

\part{Type theory}

In this part we develop type theory from the ground up. We start with a type
theory without any of the basic constructors. This is the theory of contexts
families and terms which has the basic operations of extension, weakening,
substitution and identity terms. Type theory before type constructors has not
been studied very much. Dependent product types or even universes tend to make
an early appearance in just about any presentation of type theory. While one
could argue that in type theories like the one in \cite{Dybjer1996} the type
constructors could be left out and a study of the remnants could \emph{in
principle} be carried out, this is not the usual practice. In the type theory
of \cite{TheBook}, which seems to have won the race of introducing universes
as early as possible hands down, this seems entirely unfeasible.

Nevertheless, type theory without type constructors has received some attention
recently. In \cite{Garner2014}, Garner describes the combinatorial structure
of the type operations of the weakening, substitution and projection monads
(their projections are our identity terms) and suggests lots of further research
that can be done on type theory without constructors. Also, Joyal has been
lecturing about tribes lately, which are a categorical semantics for type theory
without type constructors. Although his slides have been going around on
mailing lists, there is as of yet no easily accessible written accound on tribes.

\input{article-models-tt}

\input{article-models-ttconstr}

\input{article-models-ttmodels}
